\textbf{Sugarlike: A Language Identification Library for Low Resource Languages}

### 2013-11-05 sugarlike.tex
Update proposal, add references.

@@

Previous work on language identification has mostly be done high resource languages\footnote{e.g. http://shuyo.wordpress.com/2012/02/21/language-detection-for-twitter-with-99-1-accuracy/}. One exception is Scannell's (XXXX) indigenous tweets project. %where ....

Language identification at the word level is considered as one of the harder task because of the lack of context \{citation needed\}, especially in multilingual documents. King and Abney (2013) resolved it in a weakly supervised fashion.

@@

\begin{itemize}
\item Universal Declaration of Human Rights: almost parallel data,  needs some cleaning in ~300 language
\item Language Id Corpus (LId): character 3-grams of Crubadan corpus %there's some unknown angeled brackets
\item Crawl the tweets linked to www.indigenoustweets.com (~150 languages)
\item Crawl the blogs linked to www.indigenoustweets.com/blogs (~75 languages)
\end{itemize}

@@

\begin{itemize}
\item Baseline: Baysian model using LId corpus
\item Main model: to be decided later.
\end{itemize}

@@

>>>>

\usepackage{hyperref}

@@

Previous work on language identification has mostly be done on high resource languages\footnote{e.g. \href{http://shuyo.wordpress.com/2012/02/21/language-detection-for-twitter-with-99-1-accuracy/}{http://shuyo.wordpress.com/2012/02/21/language-detection-for-twitter-with-99-1-accuracy/}}. One exception is Scannell's indigenous tweets project \footnote{\href{www.indigenoustweets.com}{www.indigenoustweets.com}}. %where ....

Language identification at the word level is considered as one of the harder tasks because of the lack of context \footnote{citation needed}, especially in multilingual documents. King and Abney (2013 \cite{king-abney:2013}) resolved it in a weakly supervised fashion.

@@

\begin{itemize}
\item Universal Declaration of Human Rights: almost parallel data,  needs some cleaning (\~300 languages)
\item Language Id Corpus (LId): character 3-grams of Crúbadán corpus %there's some unknown angeled brackets
\item Crawl the tweets linked to www.indigenoustweets.com (\~150 languages)
\item Crawl the blogs linked to www.indigenoustweets.com/blogs (\~75 languages)
\end{itemize}

@@

\begin{itemize}
\item Baseline: Baysian model using LId corpus
\item Main model: to be decided later
\end{itemize}

@@

\
\
\
\
\

\bibliography{literature.bib}{}
\bibliographystyle{plain}
